### 2015-01-02 ex_ante_outline.tex
revise ex_ante_outline except for MRC section

%\vskip.5in
\newpage
\begin{itemize}					
	\item BUT the TA mutes lobbying incentives, even if there is ex-ante lobbying (through a couple channels, I think)
		\begin{itemize}
			\item ex-ante lobbying is more expensive: have to do it twice to get more protection than in ex-post only case

									\item This will be too expensive for some, so they won't lobby ex-ante (see Condition~\ref{ine:ea})
									\item This is part of what trade agreements do: relative to no agreement at all, raises price of protection. If only ex-post lobbying is rational, government gets control

			\item If government would set $\tau^R_{W,e}$ such that lobby can achieve $e^L$ (that is, this level is optimal for lobby), then there is no incentive to lobby ex-ante
				\begin{itemize}
					\item If gov't sets $\tau^R_{W,e}$ lower than this level, lobby cannot get $e^L$ due to differing incentives ex-ante 
						\begin{itemize}
							\item Ex-post, pays according to $\tau^N$
							\item Ex-ante, pays according to $\tau^E$
						\end{itemize}
					\item Could be higher, but not all the way to level that would achieve $e^L$ (shown below)
				\end{itemize}

	 \item It's possible that $e^{EP} < e^{L}$ with $e^{EA} > 0$

@@

			\item Not sure if $W$ concave in $\ga$ (and $\ga^* < \ga^L$) is necessary, but it seems like it
			\item $W$ concave in $\ga$ implies $W$ increases as $\pi_x$ is weighted more heavily (as in standard $W$), but eventually $W$ decreases in $\ga$
					\item Giving them more weight doesn't give gov't proportionally higher welfare
					\item Something like Bill Ethier's 2012 GJE (Political Economy Approach) paper where there are diminishing returns to lobbying as $\tau$ increases
					\item I can interpret this as $\ga$ being a concave function of $\tau$, but not sure that gets me what I need
					\item diminishing returns to lobbying in $\tau$ for lobbyists vs. diminishing returns to awarding higher $\tau$ for gov't

@@

@@

					\item Need to be up front about which assumptions (especially on $\ga$) this requires

@@

@@

\newpage
\vskip.2in
Now, add in the ex-ante lobbying \`{a} la MRC.
\begin{itemize}
	\item Maximize joint welfare of both governments and both lobbies	(instead of optimal for just govts)
	\item In MRC, there are essentially two $\ga$'s: one for ex-ante, one for ex-post
		\begin{itemize}
			\item But that doesn't match up with BS2005 framework, where the point of the TA is to take account of future $\ga$
			\item Also leads to bizarre outcome where government will take into account lobby's profits even if $e^{\text{EA}}=0$.
			\item They can max joint welfare because they have transferrable utility
			\item Something gets lost in MRC formulation about division of rents as a result of transferrable utility and this joint welfare max: they have tariff caps and strong bindings equivalent, even though these split the surplus in very different ways. There's no way to take account of this at the ex-ante stage.
		\end{itemize}
	\item To take ex-ante out of MRC, just take $x \cdot p$ out of maximand at ex-ante stage (they do it on page 1391)
		\begin{itemize}
			\item They don't treat case of immobile capital in 1998 paper, so can't compare there. But they show that there would be free trade in their model with no ex-ante bargaining (because of bargaining power assumption--lobbies have it all)
			\item I'm still not crystal clear on what purpose ex-ante lobbying serves in a world of fixed capital where gov't political welfare increases everywhere in $\ga$---here, gov't gives lobby whatever it wants ex-post
				\begin{itemize}
					\item Could $e^{EA}$ increase $\tau^{TA}$ in this world?
					\item Since TA internalized TOT externality, I think it's possible that ex-ante lobbying undoes some of that--not directly, but raises tariff above the level that is applied when TOT completely internalized. I'm not convinced though.
				\end{itemize}
		\end{itemize}
	\item Bargaining power
		\begin{itemize}
			\item It's important in MRC's story: they show how results change if they change bargaining power, and it's dramatic b/c they take an extreme view that lobbies have all the power
			\item I view bargaining power in this environment as an artificial construct---what's going on isn't really bargaining; bargaining is used as a reduced form. But it's a much more complex process
		\end{itemize}
\end{itemize}

>>>>

%\vskip.5in
\newpage

@@

@@

				\item If government would set $\tau^R_{W,e}$ such that lobby can achieve $e^L$ (that is, this level is optimal for lobby), then there is no incentive to lobby ex-ante
			\item If gov't sets $\tau^R_{W,e} < e^L$, lobby cannot get $e^L$ due to differing incentives ex-ante 
							\item Ex-post, pays according to $\tau^N$, ex-ante, pays according to $\tau^E$
					\item Could be higher, but not all the way to level that would achieve $e^L$

@@

					\item Assume throughout that $\frac{\partial \ga}{\partial e} > 0$

@@

	\item TA mutes lobbying incentives, even if there is ex-ante lobbying
			\item ex-ante lobbying is more expensive: both on the margin, and because you have to pay twice in order to get more protection than in ex-post only case
			\item This will be too expensive for some, so they won't lobby ex-ante (see Condition~\ref{ine:ea})
			\item This is part of what trade agreements do: relative to no agreement at all, raises price of protection. If only ex-post lobbying is rational, government gets control

@@

	 \item It's possible that $e^{EP} < e^{L}$ with $e^{EA} > 0$
		\begin{itemize}
			\item For instance, take $W$ concave in $\ga$ (and $\ga^* < \ga^L$)
			\item This implies $W$ increases as $\pi_x$ is weighted more heavily (as in standard $W$), but eventually $W$ decreases in $\ga$
				\begin{itemize}
					\item Giving them more weight doesn't give gov't proportionally higher welfare
					\item Something like Bill Ethier's 2012 GJE (Political Economy Approach) paper where there are diminishing returns to lobbying as $\tau$ increases
					\item I can interpret this as $\ga$ being a decreasing function of $\tau$
					%\item diminishing returns to lobbying in $\tau$ for lobbyists vs. diminishing returns to awarding higher $\tau$ for gov't
				\end{itemize}
		\end{itemize}
\end{itemize}

\newpage
\vskip.2in
Now, add in the ex-ante lobbying \`{a} la MRC.
\begin{itemize}
	\item Maximize joint welfare of both governments and both lobbies	(instead of optimal for just govts)
	\item In MRC, there are essentially two $\ga$'s: one for ex-ante, one for ex-post
		\begin{itemize}
			\item But that doesn't match up with BS2005 framework, where the point of the TA is to take account of future $\ga$
			\item Also leads to bizarre outcome where government will take into account lobby's profits even if $e^{\text{EA}}=0$.
			\item They can max joint welfare because they have transferrable utility
			\item Something gets lost in MRC formulation about division of rents as a result of transferrable utility and this joint welfare max: they have tariff caps and strong bindings equivalent, even though these split the surplus in very different ways. There's no way to take account of this at the ex-ante stage.
		\end{itemize}
	\item To take ex-ante out of MRC, just take $x \cdot p$ out of maximand at ex-ante stage (they do it on page 1391)
		\begin{itemize}
			\item They don't treat case of immobile capital in 1998 paper, so can't compare there. But they show that there would be free trade in their model with no ex-ante bargaining (because of bargaining power assumption--lobbies have it all)
			\item I'm still not crystal clear on what purpose ex-ante lobbying serves in a world of fixed capital where gov't political welfare increases everywhere in $\ga$---here, gov't gives lobby whatever it wants ex-post
				\begin{itemize}
					\item Could $e^{EA}$ increase $\tau^{TA}$ in this world?
					\item Since TA internalized TOT externality, I think it's possible that ex-ante lobbying undoes some of that--not directly, but raises tariff above the level that is applied when TOT completely internalized. I'm not convinced though.
				\end{itemize}
		\end{itemize}
	\item In MRC, no matter how tariff is set (cooperatively or non-cooperatively), contribution is $xp(\ov{t})$
		\begin{itemize}
			\item Not true in GH95
			\item In my set-up, lobby's incentives change when tariff-setting process changes
			\item In the part that is only in the NBER working paper, they have
				\begin{itemize}
					\item $z=0$ (perfectly immobile capital)
					\item no ex-ante lobbying
					\item government has all the bargaining power
					\item government sometimes chooses free trade---so there IS an incentive to use the TA as a domestic commitment device
				\end{itemize}
		\end{itemize}
	\item In MRC, weight on lobby's profits is $1+a$ no matter what. Doesn't vary in lobby's efforts. GH not really microfoundations for flexible model as in Long and Vousden (1991) / Baldwin (1987) model; microfoundations for more restrictive version with fixed weights; then decide $\tau$ to change PS, CS, etc. (p. 481 GH94). Can't get kinds of shocks as in this literature
		\begin{itemize}
			\item I still don't know exactly why you never want to reign in lobbying in GH; because it's just a conduit for information, and gov't is fully compensated for loss? But is it?
		\end{itemize}
	\item Bargaining power
		\begin{itemize}
			\item It's important in MRC's story: they show how results change if they change bargaining power, and it's dramatic b/c they take an extreme view that lobbies have all the power
			\item I view bargaining power in this environment as an artificial construct---what's going on isn't really bargaining; bargaining is used as a reduced form. But it's a much more complex process
		\end{itemize}
\end{itemize}
